The effect of detector nonlinearity on \wfa\ PSF profiles for weak gravitational lensing measurements

### 2016-04-25 ms.tex

\begin{figure}[!h]
\centering
\resizebox{\hsize}{!}{\includegraphics[page=1]{plots/f4.eps}}
\caption{Impact of spatial variability in the $\beta_0$ parameter, quantified as the standard deviation over $M=100$ realizations (for a fixed centroid) in $\Delta e_1$,  $\Delta e_2$, and $\Delta R/R$  as a function of the standard deviation $ \sigma_{\beta_0}$. 
The source magnitude is fixed at 18.3.}
\label{f4}
\end{figure}
We found that the results in Fig. \ref{f4} are insensitive to the nominal $\beta$ and therefore, in general, $\sigma_{\beta}$  can be treated as an error on $\beta$ estimation. The linear relationships in Fig. \ref{f4} also allows us to plot the slope of each curve for different magnitudes, as was done in Fig. \ref{f3}, and therefore analogous equations to Eqn. \ref{calib} can be used to derive requirements on the maximum tolerable dispersion in size and ellipticity errors given a particular set of parameters and requirements. The results are shown in Fig. \ref{f5}. We also fitted a model of the form \textbf{[MAKE NUMBERED EQ]} $\sigma_{\Delta R/ R}/ \sigma_{\beta} = A_{\text{F}}10^{B_{\text{F}} (m - m_{0})}$ (for $m_0 =20$) for the PSF size trends in Fig. \ref{f5}, as was done above for Fig. \ref{f3}. The fit parameters are presented in Table 2 as well.

%Table 2
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{Band} & \multicolumn{2}{c|}{size bias (Fig. \ref{f3})} & \multicolumn{2}{c|}{size scatter (Fig. \ref{f5})} \\
\cline{2-5}
& $A_{\text{F}} (\times 10^3)$ & $B_{\text{F}}$ & $\ A_{\text{F}} (\times 10^3)$ & $B_{\text{F}}$  \\
\hline
Y106 & 8.322 & -0.4086 & 5.057 &  -0.4045  \\
\hline
J129 & 6.958 & -0.4089  & 4.215 &  -0.4050 \\
\hline
H158 & 4.668 & -0.4069 & 2.711 &  -0.4038 \\
\hline
F184 & 2.209 & -0.4035 & 1.194 &  -0.4018 \\
\hline
\end{tabular}
\caption{Parameters resulting from fitting the curves in the upper panel of Figs. \ref{f3} and \ref{f5} to power-law functions of the form $\Delta R/ R/ \beta = A_{\text{F}}\ 10^{B_{\text{F}} (m - 20)}$ and $\sigma_{\Delta R/ R}/ \sigma_{\beta} = A_{\text{F}}\ 10^{B_{\text{F}} (m - 20)}$, respectively. \textbf{[THE x$10^3$ is confusing -- just use whole numbers?]}}
\label{table2}
\end{table}

>>>>

\begin{figure}[!h]
\centering
\resizebox{\hsize}{!}{\includegraphics[page=1]{plots/f4.eps}}
\caption{Impact of spatial variability in the $\beta_0$ parameter, quantified as the standard deviation over $M=100$ realizations (for a fixed centroid) in $\Delta e_1$,  $\Delta e_2$, and $\Delta R/R$  as a function of the standard deviation $ \sigma_{\beta_0}$. 
The source magnitude is fixed at 18.3.}
\label{f4}
\end{figure}
We found that the results in Fig. \ref{f4} are insensitive to the nominal $\beta$ and therefore, in general, $\sigma_{\beta}$  can be treated as an error on $\beta$ estimation. The linear relationships in Fig. \ref{f4} also allows us to plot the slope of each curve for different magnitudes, as was done in Fig. \ref{f3}, and therefore analogous equations to Eqn. \ref{calib} can be used to derive requirements on the maximum tolerable dispersion in size and ellipticity errors given a particular set of parameters and requirements. The results are shown in Fig. \ref{f5}. We also fitted a model of the form 
\begin{align}
\frac{\sigma_{\Delta R/ R}} {\sigma_{\beta}} = A_{\text{F}}10^{B_{\text{F}} (m - m_{0})} \ (m_0 =20)
\end{align}
for the PSF size trends in Fig. \ref{f5}, as was done above for Fig. \ref{f3} (\emph{c.f.}, Eqn. \ref{power_law}). The fit parameters are presented in Table 2 as well.

%Table 2
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{Band} & \multicolumn{2}{c|}{size bias (Fig. \ref{f3})} & \multicolumn{2}{c|}{size scatter (Fig. \ref{f5})} \\
\cline{2-5}
& $A_{\text{F}}$ & $B_{\text{F}}$ & $\ A_{\text{F}}$ & $B_{\text{F}}$  \\
\hline
Y106 & 8322 & -0.4086 & 5057 &  -0.4045  \\
\hline
J129 & 6958 & -0.4089  & 4215 &  -0.4050 \\
\hline
H158 & 4668 & -0.4069 & 2711 &  -0.4038 \\
\hline
F184 & 2209 & -0.4035 & 1194 &  -0.4018 \\
\hline
\end{tabular}
\caption{Parameters resulting from fitting the curves in the upper panel of Figs. \ref{f3} and \ref{f5} to power-law functions of the form $\Delta R/ R/ \beta = A_{\text{F}}\ 10^{B_{\text{F}} (m - 20)}$ and $\sigma_{\Delta R/ R}/ \sigma_{\beta} = A_{\text{F}}\ 10^{B_{\text{F}} (m - 20)}$, respectively.}
\label{table2}
\end{table}
